From physical principles to ???

### 2016-04-22 2015CompleteDerivation/completeDerivation.tex
Cleaned up leading up to rationale for classical assumption

Before discussing time evolution, we should investigate what assuming our state is infinitesimally reducible means in terms of the fundamental model discussed in Assumption \ref{detrevass}.

@@

% Det/rev for infinitesimal part
% Inconsistent: 1. X=AxB A'=F(A) B'=F(B) Isolated sub-systems. Does not work for measuring. 2. A'=F(A) B'=F(A,B) Ideal non-interfering measurement: deterministic but not reversible. 3. A'=F(A,B) B'=F(A,B) X det/rev whole, but A not deterministic itself. But if you consider X a sub-system of X and something else, you can make the same argument. Whole universe deterministic, but none of its parts. 4. A=As x Au ; B=Bs x Bu ; As' = F(As) Au=F(X) Bu=F(X) Bs = F(As, Au) ; more realistic picture. Still non-reversible (if As' = F(As), then nothing else can be F(As) and have bijective map).

We further characterize the relationship between the whole and the parts with the following assumption:

@@

In other words: if we know the state and the evolution for the whole system, we also know the evolution for all its parts; if we know the state and evolution for all the parts, we know the state and the evolution for the whole system. By smaller we do not mean spatial extent, but of smaller amount (e.g. less mass): even at the same spatial location we can imagine that there are infinitely many components (e.g. the mass, as a number, is continuously divisible(.

\begin{rationale}

	% 1. We need a process that can interact with parts
	% 2. State cannot be full description. Cannot stop interacting with the rest of the universe, we need unstated part to keep interacting (no measurement)
	% 3. Complete isolation means no single universe. Cannot have meaningful determinism at different level of scale.
	% 4. Evolution that exchange information means systems cannot always be isolated
	% 5. It's an approximation. But the approximation breaks down the more the assumption is taken literally. The two cases that can make the assumption hold break down in the case of infinitesimal pieces. The set of states of the described object is "big" compared to the set of states of the probe. If both infinitesimal homogeneous pieces, that cannot hold. The laws are not symmetric so that the probe is more affecte by the system under sudy. If both infinitesimal homogeneous pieces, the law is symmetric.
	% 6. A detrev system can't tell time.

	% x = v_0 t + x_0 
	% v = v_0

	% Problems. Due to parts that are independent
	%           Due to parts that are infinitesimal
	%           Due to everything is state

	% 1. Need a process for parts, not always have it. (1)
	% 2. Isolation (and detrev) becomes untenable as parts are infinitesimal (5)
	% 3. If it were tenable, we would have separate universes (2,3,4)
	%    Detrev individual parts are not part of same universe (3)
	%    If parts interact deterministically, still no good: can (2) decompose locally in d.o.f. And infinitesimal parts are local
	%    Completely detrev system cannot be interacted with
	% => Tension between two desires: system is isolated so that we can define independent state, system is not isolated so that we can interact with it.
	% 4. A system that is detrev at all levels cannot tell time (6)

	This is clearly a \emph{simplifying} assumption, and it is instructive to understand when it breaks down.

>>>>

@@

Now that we have fully characterized what we mean by a classical system, we can now stipulate the following:

@@

\begin{rationale}
	The idea is that time evolution specifies a map for the state space $\mathcal{S}$ of the infinitesimal parts. And knowing how the parts evolve, we also know how to evolve the whole, that elements in $\mathcal{C}$.

	Consistently with what we said in Assumption \ref{detrevass}, if we defined a state for the infinitesimal parts, then one such deterministic and reversible evolution should exist. Yet, the idea that we can assign states to infinitesimal parts should be considered only a \emph{simplifying} assumption, and it is instructive to understand when it breaks down.
